---
title: "Quotient Space Learning Benchmark Results"
subtitle: "Comparative Analysis of Optimization Methods for Patient Subgroup Discovery"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: hide
    fig_width: 12
    fig_height: 8
  pdf_document:
    toc: true
    number_sections: true
    fig_width: 10
    fig_height: 6
params: 
  useRealData: FALSE
  useNumericMetrics: TRUE
knit: |
  (function(inputFile, encoding) { 
    # Determine output filename based on parameters
    yaml_params <- rmarkdown::yaml_front_matter(inputFile)$params
    data_type <- ifelse(yaml_params$useRealData, "real", "dummy")
    numeric_type <- ifelse(yaml_params$useNumericMetrics, "with_numeric", "no_numeric")
    output_subdir <- paste0(data_type, "_", numeric_type, "_data")
    
    # Create reports subdirectory
    reports_subdir <- here::here("report")
    if (!dir.exists(reports_subdir)) {
      dir.create(reports_subdir, recursive = TRUE)
    }
    
    # Generate output filename in the subdirectory
    pSubTitle <- file.path(reports_subdir, paste0('benchmark_visualisation_', output_subdir, '.html'))

    rmarkdown::render( 
      input = inputFile, 
      encoding = encoding, 
      output_file = pSubTitle
    )
  })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE,
  fig.width = 9,
  fig.height = 6,
  dpi = 300
)

# Load required libraries
suppressMessages(library(here))
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
suppressMessages(library(tidyr))
suppressMessages(library(plotly))
suppressMessages(library(knitr))
suppressMessages(library(kableExtra))
suppressMessages(library(gridExtra))
suppressMessages(library(htmlwidgets))

# Create directories and setup saving functions
base_plots_dir <- here::here("plots")
base_tables_dir <- here::here("tables")
base_reports_dir <- here::here("report")

# Will be set after config chunk runs
plots_dir <- NULL
tables_dir <- NULL
reports_dir <- NULL

# Function to save plots
save_plot <- function(plot_obj, filename, width = 8, height = 6, data_suffix = NULL) {
  if (is.null(data_suffix)) {
    data_suffix <- ifelse(exists("output_subdir"), output_subdir, "dummy_no_numeric_data")
  }
  full_filename <- paste0(filename, ".png")
  filepath <- file.path(plots_dir, full_filename)
  
  if ("plotly" %in% class(plot_obj)) {
    # For plotly objects, save as HTML and also try to save as static image
    html_path <- file.path(plots_dir, paste0(filename, ".html"))
    htmlwidgets::saveWidget(plot_obj, html_path, selfcontained = TRUE)
    cat("Saved interactive plot:", html_path, "\n")
  } else {
    # For ggplot objects
    ggsave(filepath, plot_obj, width = width, height = height, dpi = 300)
    cat("Saved plot:", filepath, "\n")
  }
}

# Function to save tables
save_table <- function(table_data, filename, format = "csv") {
  if (format == "csv") {
    filepath <- file.path(tables_dir, paste0(filename, ".csv"))
    write.csv(table_data, filepath, row.names = FALSE)
  } else if (format == "rds") {
    filepath <- file.path(tables_dir, paste0(filename, ".rds"))
    saveRDS(table_data, filepath)
  }
  cat("Saved table:", filepath, "\n")
  return(filepath)
}
```

# Configuration

```{r config}
# Set this to match the data type you want to visualize
useRealData <- params$useRealData  # Set to TRUE for real data results, FALSE for dummy data results
useNumericMetrics <- params$useNumericMetrics  # Set to match numeric_metrics setting in run_methods.R
numeric_flag <- ifelse(useNumericMetrics, "with_numeric", "no_numeric")
data_type_suffix <- paste0(ifelse(useRealData, "real", "dummy"), "_", numeric_flag, "_data")
output_subdir <- data_type_suffix  # This matches the subdirectory structure from run_methods.R

# Create subdirectories for organized output
plots_dir <- file.path(base_plots_dir, output_subdir)
tables_dir <- file.path(base_tables_dir, output_subdir)
reports_dir <- file.path(base_reports_dir)

# Create directories if they don't exist
for (dir_path in c(plots_dir, tables_dir, reports_dir)) {
  if (!dir.exists(dir_path)) {
    dir.create(dir_path, recursive = TRUE)
  }
}

cat("Analysis Configuration:",
    paste("Data Type:", ifelse(useRealData, "Real Data", "Dummy Data")),
    paste("Numeric Metrics:", ifelse(useNumericMetrics, "Enabled", "Disabled")),
    paste("Output Directory:", paste0("output/", output_subdir, "/")),
    paste("Plots Directory:", plots_dir),
    paste("Tables Directory:", tables_dir),
    paste("Reports Directory:", reports_dir),
    sep = "\n")
```

# Load Results

```{r load-results}
# Check if saved results exist
fitness_file <- here::here(paste0('output/', output_subdir, '/all_comparison_fitness_data.rds'))
times_file <- here::here(paste0('output/', output_subdir, '/all_comparison_times_data.rds'))
plot_file <- here::here(paste0('output/', output_subdir, '/all_comparison_data_for_3d_plot.rds'))

if (!file.exists(fitness_file)) {
  stop(paste0("Results not found for ", ifelse(useRealData, "real data", "dummy data"), 
              ".\nExpected file: ", fitness_file,
              "\nPlease run run_methods.R first with useRealData = ", useRealData, " to generate the results."))
}

all_comparison_fitness_data = readRDS(fitness_file)
all_comparison_times_data = readRDS(times_file)
all_comparison_data_for_3d_plot = readRDS(plot_file)

# Transform method names to avoid confusion 
if ("Method" %in% colnames(all_comparison_fitness_data)) {
  all_comparison_fitness_data$Method <- gsub("Genetic Algorithm", "GA (No Quotient Space)", all_comparison_fitness_data$Method)
  all_comparison_fitness_data$Method <- gsub("Orbit-Aware GA", "GA (With Quotient Space)", all_comparison_fitness_data$Method)
  all_comparison_fitness_data$Method <- gsub("Bayesian Optimization \\(No Orbits\\)", "BO (No Quotient Space)", all_comparison_fitness_data$Method)
  all_comparison_fitness_data$Method <- gsub("Bayesian Optimization \\(With Orbits\\)", "BO (With Quotient Space)", all_comparison_fitness_data$Method)
}
if ("Method" %in% colnames(all_comparison_times_data)) {
  all_comparison_times_data$Method <- gsub("Genetic Algorithm", "GA (No Quotient Space)", all_comparison_times_data$Method)
  all_comparison_times_data$Method <- gsub("Orbit-Aware GA", "GA (With Quotient Space)", all_comparison_times_data$Method)
  all_comparison_times_data$Method <- gsub("Bayesian Optimization \\(No Orbits\\)", "BO (No Quotient Space)", all_comparison_times_data$Method)
  all_comparison_times_data$Method <- gsub("Bayesian Optimization \\(With Orbits\\)", "BO (With Quotient Space)", all_comparison_times_data$Method)
}
if ("Method" %in% colnames(all_comparison_data_for_3d_plot)) {
  all_comparison_data_for_3d_plot$Method <- gsub("Genetic Algorithm", "GA (No Quotient Space)", all_comparison_data_for_3d_plot$Method)
  all_comparison_data_for_3d_plot$Method <- gsub("Orbit-Aware GA", "GA (With Quotient Space)", all_comparison_data_for_3d_plot$Method)
  all_comparison_data_for_3d_plot$Method <- gsub("Bayesian Optimization \\(No Orbits\\)", "BO (No Quotient Space)", all_comparison_data_for_3d_plot$Method)
  all_comparison_data_for_3d_plot$Method <- gsub("Bayesian Optimization \\(With Orbits\\)", "BO (With Quotient Space)", all_comparison_data_for_3d_plot$Method)
}

# Load the saved datasets
cat("Loading analysis results for", ifelse(useRealData, "real data", "dummy data"), "...",
    "Successfully loaded:",
    sprintf("  - Fitness data: %d rows, %d columns", nrow(all_comparison_fitness_data), ncol(all_comparison_fitness_data)),
    sprintf("  - Times data: %d rows, %d columns", nrow(all_comparison_times_data), ncol(all_comparison_times_data)),
    sprintf("  - 3D plot data: %d rows, %d columns", nrow(all_comparison_data_for_3d_plot), ncol(all_comparison_data_for_3d_plot)),
    sep = "\n")

# Debug: Check column names and data structure
cat("\nData validation:\n")
cat("Fitness data columns:", paste(colnames(all_comparison_fitness_data), collapse = ", "), "\n")
cat("3D plot data columns:", paste(colnames(all_comparison_data_for_3d_plot), collapse = ", "), "\n")

# Check if Method column exists and show unique values
if ("Method" %in% colnames(all_comparison_data_for_3d_plot)) {
  cat("Unique methods in 3D data:", paste(unique(all_comparison_data_for_3d_plot$Method), collapse = ", "), "\n")
} else {
  cat("WARNING: Method column not found in 3D plot data!\n")
}

# Load exhaustive search results (if available)
exhaustive_file <- here::here(paste0('output/', output_subdir, '/exhaustive_search_global_optima.rds'))
exhaustive_data_available <- FALSE
exhaustive_global_optima <- NULL

if (file.exists(exhaustive_file)) {
  exhaustive_global_optima <- readRDS(exhaustive_file)
  
  # Check if we have valid exhaustive search results
  valid_exhaustive_results <- sum(!is.na(exhaustive_global_optima$TrueGlobalOptimum))
  
  if (valid_exhaustive_results > 0) {
    exhaustive_data_available <- TRUE
    cat(sprintf("  - Exhaustive search results: %d rows (%d with valid optima)\n", 
                nrow(exhaustive_global_optima), valid_exhaustive_results))
    
    # Create enhanced comparison data with optimality gaps
    all_comparison_fitness_data_with_gaps <- all_comparison_fitness_data %>%
      left_join(exhaustive_global_optima %>% select(MinSubgroupSize, TrueGlobalOptimum), 
               by = "MinSubgroupSize") %>%
      mutate(
        OptimalityGap = ifelse(!is.na(TrueGlobalOptimum), 
                             (TrueGlobalOptimum - OptimalFitness) / TrueGlobalOptimum * 100, 
                             NA),
        PerformanceRatio = ifelse(!is.na(TrueGlobalOptimum), 
                                OptimalFitness / TrueGlobalOptimum, 
                                NA)
      )
    
    cat("  - Enhanced fitness data with optimality gaps computed\n")
  } else {
    cat("  - Exhaustive search file found but no valid results available\n")
  }
} else {
  cat("  - No exhaustive search results available (discrete optimization cases only)\n")
}
```

# Performance Summary

```{r performance-summary}
# Generate basic performance summary without statistical analysis
methods_summary <- all_comparison_data_for_3d_plot %>%
  group_by(Method) %>%
  summarise(
    n_runs = n(),
    # Fitness statistics
    avg_fitness = round(mean(OptimalFitness, na.rm = TRUE), 4),
    std_fitness = round(sd(OptimalFitness, na.rm = TRUE), 4),
    min_fitness = round(min(OptimalFitness, na.rm = TRUE), 4),
    max_fitness = round(max(OptimalFitness, na.rm = TRUE), 4),
    # Time statistics
    avg_time = round(mean(Time_Seconds, na.rm = TRUE), 2),
    std_time = round(sd(Time_Seconds, na.rm = TRUE), 2),
    .groups = 'drop'
  ) %>%
  arrange(desc(avg_fitness))

# Create basic summary table
kable(methods_summary, 
      caption = paste("Performance Summary -", ifelse(useRealData, "Real Data", "Dummy Data")),
      col.names = c("Method", "Runs", "Mean Fitness", "Std Fitness", "Min Fitness", "Max Fitness", "Mean Time", "Std Time")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE) %>%
  row_spec(1, bold = TRUE, background = "#e8f5e8")  # Highlight best performer

# Key insights
best_method <- methods_summary$Method[1]
fastest_method <- methods_summary$Method[which.min(methods_summary$avg_time)]
most_consistent <- methods_summary$Method[which.min(methods_summary$std_fitness)]

cat("\nKey Performance Insights:\n")
cat("• Best Mean Fitness:", best_method, "(", methods_summary$avg_fitness[1], ")\n")
cat("• Fastest Mean Time:", fastest_method, "(", min(methods_summary$avg_time), "seconds)\n")

# Add optimality gap insights if available
if (exhaustive_data_available && exists("all_comparison_fitness_data_with_gaps")) {
  gap_insights <- all_comparison_fitness_data_with_gaps %>%
    filter(!is.na(OptimalityGap)) %>%
    group_by(Method) %>%
    summarise(mean_gap = mean(OptimalityGap, na.rm = TRUE), .groups = 'drop') %>%
    arrange(mean_gap)
  
  if (nrow(gap_insights) > 0) {
    best_gap_method <- gap_insights$Method[1]
    best_gap_value <- round(gap_insights$mean_gap[1], 2)
    
    cat("• Closest to Global Optimum:", best_gap_method, "(", best_gap_value, "% gap)\n")
    cat("• Theoretical Validation: Exhaustive search available for discrete cases\n")
  }
}
```

# Exhaustive Search Validation

```{r exhaustive-search-analysis, eval=exhaustive_data_available, results = 'asis'}
if (exhaustive_data_available && exists("exhaustive_global_optima") && !is.null(exhaustive_global_optima)) {
  cat("## Performance Relative to Theoretical Global Optimum\n\n")
  cat("This analysis shows the performance of each optimization method relative to the theoretical global optimum (higher is better).\n\n")
  # Calculate performance summary by method
  valid_gap_data <- all_comparison_fitness_data_with_gaps %>%
    filter(!is.na(OptimalityGap))
  if (nrow(valid_gap_data) > 0) {
    perf_summary <- valid_gap_data %>% 
      group_by(Method) %>% 
      mutate(flagGlobalOptimumReached = ifelse(abs(TrueGlobalOptimum - OptimalFitness) < 0.00001, TRUE, FALSE)) %>% 
      summarise(meanPerformanceRatio = mean(PerformanceRatio), 
                medianPerformanceRatio = median(PerformanceRatio), 
                pctGlobalOptimumReached = sum(flagGlobalOptimumReached)/n(), 
                .groups = 'drop') %>% 
      mutate_if(is.numeric, round, digits = 4)
    # Display performance table
    print(kable(perf_summary, 
          caption = "Performance Relative to Theoretical Global Optimum by Method (Higher is Better)",
          col.names = c("Method", 'Mean Performance Ratio', 'Median Performance Ratio', '% of Global Optimum Reached')) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE) %>%
      row_spec(1, bold = TRUE, background = "#e8f5e8"))  # Highlight best performer
  } else {
    cat("No valid performance data available.\n")
  }
}
```

```{r optimality-gap-visualization, eval=exhaustive_data_available, fig.cap="Optimality gap distribution by method showing distance from theoretical global optimum"}
if (exhaustive_data_available && exists("all_comparison_fitness_data_with_gaps") && !is.null(all_comparison_fitness_data_with_gaps)) {
  valid_gap_data <- all_comparison_fitness_data_with_gaps %>%
    filter(!is.na(OptimalityGap))
  
    # Performance ratio plot (alternative view)
    valid_ratio_data <- all_comparison_fitness_data_with_gaps %>%
      filter(!is.na(PerformanceRatio))
    
    if (nrow(valid_ratio_data) > 0) {
      ratio_plot <- valid_ratio_data %>%
        ggplot(aes(x = reorder(Method, PerformanceRatio, median), y = PerformanceRatio, fill = Method)) +
        geom_boxplot(alpha = 0.7, outlier.shape = NA) +
        geom_jitter(width = 0.2, alpha = 0.5, size = 0.8) +
        geom_hline(yintercept = 1.0, linetype = "dashed", color = "red", alpha = 0.7) +
        labs(
          title = "Performance Ratio Distribution by Method",
          subtitle = "Ratio of achieved fitness to theoretical global optimum (higher is better)",
          x = "Method",
          y = "Performance Ratio (Achieved/Optimal)",
          caption = "Red line shows perfect performance (ratio = 1.0)"
        ) +
        theme_minimal() +
        theme(
          axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none",
          plot.title = element_text(size = 14, face = "bold"),
          plot.subtitle = element_text(size = 12)
        ) +
        scale_fill_brewer(type = "qual", palette = "Set2") +
        ylim(0, 1.05)
      
      print(ratio_plot)
      save_plot(ratio_plot, "performance_ratio_distribution", width = 10, height = 6)
      
      # Global Optimum Achievement Analysis
      cat("\n### Global Optimum Achievement Analysis\n")
      
      global_optimum_analysis <- valid_ratio_data %>% 
        group_by(Method) %>% 
        mutate(flagGlobalOptimumReached = ifelse(abs(TrueGlobalOptimum - OptimalFitness) < 0.00001, TRUE, FALSE)) %>% 
        summarise(
          meanPerformanceRatio = round(mean(PerformanceRatio), 4), 
          medianPerformanceRatio = round(median(PerformanceRatio), 4), 
          pctGlobalOptimumReached = round(sum(flagGlobalOptimumReached)/n() * 100, 2),
          nCases = n(),
          nOptimumReached = sum(flagGlobalOptimumReached),
          .groups = 'drop'
        ) %>%
        arrange(desc(pctGlobalOptimumReached), desc(meanPerformanceRatio))
      
      # Display the analysis table
      kable(global_optimum_analysis, 
            caption = "Global Optimum Achievement Analysis by Method",
            col.names = c("Method", "Mean Ratio", "Median Ratio", "% Global Optimum Reached", "Total Cases", "Optimum Reached (Count)")) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE) %>%
        row_spec(1, bold = TRUE, background = "#e8f5e8")  # Highlight best performer
      
      # Save the analysis results
      save_table(global_optimum_analysis, "global_optimum_achievement_analysis", format = "csv")
      
      # Key insights
      best_optimum_method <- global_optimum_analysis$Method[1]
      best_optimum_pct <- global_optimum_analysis$pctGlobalOptimumReached[1]
      total_optimum_reached <- sum(global_optimum_analysis$nOptimumReached)
      total_cases <- sum(global_optimum_analysis$nCases)
      overall_success_rate <- round(total_optimum_reached / total_cases * 100, 2)
      
      cat("\n**Key Global Optimum Insights:**\n")
      cat("• Best success rate:", best_optimum_method, "(", best_optimum_pct, "% of cases)\n")
      cat("• Overall success rate across all methods:", overall_success_rate, "%\n")
      cat("• Total cases where global optimum was reached:", total_optimum_reached, "out of", total_cases, "\n")
      
      # Method-specific breakdown
      cat("\n**Method Performance Breakdown:**\n")
      for (i in 1:nrow(global_optimum_analysis)) {
        row <- global_optimum_analysis[i, ]
        cat(sprintf("• %s: %.2f%% success rate (%.4f mean ratio, %d/%d cases)\n", 
                   row$Method, row$pctGlobalOptimumReached, row$meanPerformanceRatio, 
                   row$nOptimumReached, row$nCases))
      }
  } else {
    cat("No valid gap data available for visualization.\n")
  }
}
```

```{r gap-vs-subgroup-size, eval=exhaustive_data_available, fig.cap="Optimality gap trends across different minimum subgroup sizes"}
if (exhaustive_data_available && exists("all_comparison_fitness_data_with_gaps") && !is.null(all_comparison_fitness_data_with_gaps)) {
  valid_gap_data <- all_comparison_fitness_data_with_gaps %>%
    filter(!is.na(OptimalityGap))
  
  if (nrow(valid_gap_data) > 0) {
    # Plot performance relative to optimum vs minimum subgroup size
    perf_trend_plot <- valid_gap_data %>%
      ggplot(aes(x = MinSubgroupSize, y = 1 - OptimalityGap/100, color = Method)) +
      geom_point(alpha = 0.2, size = 1.5) +
      labs(
        title = "Performance Relative to Optimum vs Minimum Subgroup Size",
        subtitle = "How method performance varies with problem constraint difficulty",
        x = "Minimum Subgroup Size",
        y = "Performance Relative to Optimum",
        color = "Method"
      ) +
      theme_minimal() +
      theme(
        legend.position = "bottom",
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12)
      ) +
      scale_color_brewer(type = "qual", palette = "Set2") +
      guides(color = guide_legend(nrow = 2))
    print(perf_trend_plot)
    save_plot(perf_trend_plot, "performance_vs_subgroup_size", width = 10, height = 6)
  } else {
    cat("No valid gap data available for trend analysis.\n")
  }
}
```

# 3D Performance Visualization

This interactive 3D plot shows the relationship between minimum subgroup size, optimal fitness, and execution time across all methods.

```{r 3d-plot, fig.cap="Interactive 3D visualization of method performance across all evaluation criteria", fig.height=6}
# Create the 3D scatter plot using Plotly
p_3d_comparison <- plot_ly(
  all_comparison_data_for_3d_plot %>% group_by(Method, ParamSet),
  x = ~MinSubgroupSize,
  y = ~OptimalFitness,
  z = ~Time_Seconds,
  color = ~Method,
  colors = c("red", "blue", "purple", "green", "orange", "cyan"),
  type = "scatter3d",
  mode = "lines+markers",
  marker = list(size = 3, opacity = 0.6),
  line = list(width = 2, opacity = 0.3),
  text = ~paste(
    "Method:", Method,
    "<br>Min Subgroup Size:", MinSubgroupSize,
    "<br>Optimal Fitness:", round(OptimalFitness, 4),
    "<br>Execution Time:", round(Time_Seconds, 2), "s"
  ),
  hoverinfo = "text"
) %>%
  layout(
    title = paste("Performance Landscape -", ifelse(useRealData, "Real Data", "Dummy Data")),
    scene = list(
      xaxis = list(title = "Minimum Subgroup Size"),
      yaxis = list(title = "Optimal Fitness Value"),
      zaxis = list(title = "Execution Time (Seconds)")
    ),
    width = 800,
    height = 500
  )

p_3d_comparison

# Save the 3D plot
save_plot(p_3d_comparison, "3d_performance_landscape")
```


# Method Comparisons

## GA: No Quotient Space vs With Quotient Space

```{r ga-comparison, fig.cap="Comparison between standard GA and quotient-space-aware GA approaches"}
# GA vs Quotient-Space-Aware GA Analysis
dfPlt_GA <- all_comparison_data_for_3d_plot %>% 
  filter(Method %in% c('GA (No Quotient Space)', 'GA (With Quotient Space)'))

if (nrow(dfPlt_GA) > 0) {
  
  # Performance comparison
  p_ga_fitness <- ggplot(dfPlt_GA, aes(x = MinSubgroupSize, y = OptimalFitness, color = Method)) +
    geom_jitter(alpha = 0.2, size = 1, height = 0.001) +
    # geom_smooth(method = "loess", se = TRUE, alpha = 0.2) +
    labs(title = "GA Performance Comparison",
         x = "Minimum Subgroup Size",
         y = "Optimal Fitness") +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  # Time comparison
  p_ga_time <- ggplot(dfPlt_GA, aes(x = Method, y = Time_Seconds, fill = Method)) +
    geom_boxplot(alpha = 0.7) +
    # geom_jitter(width = 0.2, alpha = 0.5) +
    labs(title = "Execution Time Distribution",
         x = "Method",
         y = "Execution Time (Seconds)") +
    theme_minimal() +
    theme(legend.position = "none")

  # Save combined plot
  combined_ga_plot <- grid.arrange(p_ga_fitness, p_ga_time, ncol = 2)
  save_plot(combined_ga_plot, "ga_combined_comparison", 8, 6)
  
  # Enhanced summary statistics with statistical testing
  ga_summary <- dfPlt_GA %>%
    group_by(Method) %>%
    summarise(
      n_runs = n(),
      avg_fitness = round(mean(OptimalFitness), 4),
      std_fitness = round(sd(OptimalFitness), 4),
      avg_time = round(mean(Time_Seconds), 2),
      std_time = round(sd(Time_Seconds), 2),
      .groups = 'drop'
    )
  
  kable(ga_summary, caption = "GA Methods Comparison with Standard Deviations") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
  # Statistical comparison between GA methods
  ga_no_quotient_space <- dfPlt_GA %>% filter(Method == 'GA (No Quotient Space)')
  ga_with_quotient_space <- dfPlt_GA %>% filter(Method == 'GA (With Quotient Space)')
  
  if (nrow(ga_no_quotient_space) > 0 && nrow(ga_with_quotient_space) > 0) {
    # Fitness comparison
    fitness_test <- wilcox.test(ga_with_quotient_space$OptimalFitness, ga_no_quotient_space$OptimalFitness, paired = FALSE)
    
    # Time comparison  
    time_test <- wilcox.test(ga_with_quotient_space$Time_Seconds, ga_no_quotient_space$Time_Seconds, paired = FALSE)
    
    # Effect sizes (Cohen's d)
    fitness_pooled_sd <- sqrt((var(ga_with_quotient_space$OptimalFitness) + var(ga_no_quotient_space$OptimalFitness)) / 2)
    fitness_cohens_d <- (mean(ga_with_quotient_space$OptimalFitness) - mean(ga_no_quotient_space$OptimalFitness)) / fitness_pooled_sd
    
    time_pooled_sd <- sqrt((var(ga_with_quotient_space$Time_Seconds) + var(ga_no_quotient_space$Time_Seconds)) / 2)
    time_cohens_d <- (mean(ga_with_quotient_space$Time_Seconds) - mean(ga_no_quotient_space$Time_Seconds)) / time_pooled_sd
    
    cat("\n**Statistical Analysis - GA Quotient Space Learning Effect:**\n")
    cat("• Fitness improvement: p =", format.pval(fitness_test$p.value), ", Cohen's d =", round(fitness_cohens_d, 3), "\n")
    cat("• Time cost: p =", format.pval(time_test$p.value), ", Cohen's d =", round(time_cohens_d, 3), "\n")
    
    if (fitness_test$p.value < 0.05) {
      cat("• **Significant fitness improvement** with quotient space learning\n")
    }
    if (time_test$p.value < 0.05) {
      cat("• **Significant time cost** for quotient space learning\n")
    }
  }
  
} else {
  cat("Note: GA comparison data not available in current results\n")
}
```

## BO: No Quotient Space vs With Quotient Space

```{r bo-comparison, fig.cap="Comparison between standard BO and quotient-space-enhanced BO approaches"}
# BO comparison
dfPlt_BO <- all_comparison_data_for_3d_plot %>% 
  filter(Method %in% c('BO (No Quotient Space)', 'BO (With Quotient Space)'))

if (nrow(dfPlt_BO) > 0) {
  # Performance comparison
  p_bo_fitness <- ggplot(dfPlt_BO, aes(x = MinSubgroupSize, y = OptimalFitness, color = Method)) +
    geom_jitter(alpha = 0.2, size = 1, height = 0.01) +
    # geom_smooth(method = "loess", se = TRUE, alpha = 0.2) +
    labs(title = "BO Performance Comparison",
         x = "Minimum Subgroup Size",
         y = "Optimal Fitness") +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  # Time comparison
  p_bo_time <- ggplot(dfPlt_BO, aes(x = Method, y = Time_Seconds, fill = Method)) +
    geom_boxplot(alpha = 0.7) +
    # geom_jitter(width = 0.2, alpha = 0.5) +
    labs(title = "Execution Time Distribution",
         x = "Method",
         y = "Execution Time (Seconds)") +
    theme_minimal() +
    theme(legend.position = "none")
  
  # Save combined plot
  combined_bo_plot <- grid.arrange(p_bo_fitness, p_bo_time, ncol = 2)
  save_plot(combined_bo_plot, "bo_combined_comparison", 8, 6)
  
  # Enhanced summary statistics with statistical testing
  bo_summary <- dfPlt_BO %>%
    group_by(Method) %>%
    summarise(
      n_runs = n(),
      avg_fitness = round(mean(OptimalFitness), 4),
      std_fitness = round(sd(OptimalFitness), 4),
      avg_time = round(mean(Time_Seconds), 2),
      std_time = round(sd(Time_Seconds), 2),
      .groups = 'drop'
    )
  
  kable(bo_summary, caption = "BO Methods Comparison with Standard Deviations") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
  # Statistical comparison between BO methods
  bo_no_quotient_space <- dfPlt_BO %>% filter(Method == 'BO (No Quotient Space)')
  bo_with_quotient_space <- dfPlt_BO %>% filter(Method == 'BO (With Quotient Space)')
  
  if (nrow(bo_no_quotient_space) > 0 && nrow(bo_with_quotient_space) > 0) {
    # Fitness comparison
    fitness_test <- wilcox.test(bo_with_quotient_space$OptimalFitness, bo_no_quotient_space$OptimalFitness, paired = FALSE)
    
    # Time comparison  
    time_test <- wilcox.test(bo_with_quotient_space$Time_Seconds, bo_no_quotient_space$Time_Seconds, paired = FALSE)
    
    # Effect sizes (Cohen's d)
    fitness_pooled_sd <- sqrt((var(bo_with_quotient_space$OptimalFitness) + var(bo_no_quotient_space$OptimalFitness)) / 2)
    fitness_cohens_d <- (mean(bo_with_quotient_space$OptimalFitness) - mean(bo_no_quotient_space$OptimalFitness)) / fitness_pooled_sd
    
    time_pooled_sd <- sqrt((var(bo_with_quotient_space$Time_Seconds) + var(bo_no_quotient_space$Time_Seconds)) / 2)
    time_cohens_d <- (mean(bo_with_quotient_space$Time_Seconds) - mean(bo_no_quotient_space$Time_Seconds)) / time_pooled_sd
    
    cat("\n**Statistical Analysis - BO Quotient Space Learning Effect:**\n")
    cat("• Fitness change: p =", format.pval(fitness_test$p.value), ", Cohen's d =", round(fitness_cohens_d, 3), "\n")
    cat("• Time change: p =", format.pval(time_test$p.value), ", Cohen's d =", round(time_cohens_d, 3), "\n")
    
    if (abs(fitness_cohens_d) > 0.2) {
      cat("• Effect size indicates", ifelse(fitness_cohens_d > 0, "improvement", "degradation"), "with quotient space learning\n")
    } else {
      cat("• Minimal effect of quotient space learning on BO performance\n")
    }
  }
    
} else {
  cat("Note: Bayesian Optimization data not available in current results\n")
}
```

# Overall Method Comparison

## Performance vs Subgroup Size

```{r overall-performance, fig.cap="Overall performance comparison across all methods"}
# Define distinct colors for each method with maximum contrast
method_colors <- c(
  "GA (With Quotient Space)" = "#FF0000",      # Pure Red
  "GA (No Quotient Space)" = "#000000",        # Black  
  "BO (With Quotient Space)" = "#0000FF",      # Pure Blue
  "BO (No Quotient Space)" = "#00FF00",        # Pure Green
  "Greedy Algorithm" = "#00FFFF"       # Pure Cyan
)

p_methods_comparison <- ggplot(all_comparison_data_for_3d_plot, aes(x = MinSubgroupSize, y = OptimalFitness, color = Method)) +
  geom_point(alpha = 0.5, size = 1) +
  # geom_smooth(method = "loess", se = TRUE, alpha = 0.2) +
  scale_color_manual(values = method_colors) +
  labs(title = paste("Performance Comparison Across All Methods \n-", 
                     ifelse(useRealData, "Real Data", "Dummy Data"),
                     ifelse(useNumericMetrics, "with Numeric Variables", "without Numeric Variables")),
       x = "Minimum Subgroup Size",
       y = "Optimal Fitness") +
  theme_minimal()
  # theme(legend.position = "bottom")

print(p_methods_comparison)

# Save overall methods comparison plot
save_plot(p_methods_comparison, "overall_methods_comparison", 8, 6)
```

## Execution Time Analysis

```{r time-analysis, fig.cap="Execution time distribution and efficiency analysis"}
# Time distribution by method
p_time_comparison <- ggplot(all_comparison_data_for_3d_plot, aes(x = Method, y = Time_Seconds, fill = Method)) +
  geom_boxplot(alpha = 0.7) +
  # geom_jitter(width = 0.2, alpha = 0.4, size = 0.8) +
  scale_fill_manual(values = method_colors) +
  labs(title = paste("Execution Time Distribution by Method -", 
                     ifelse(useRealData, "Real Data", "Dummy Data"),
                     ifelse(useNumericMetrics, "with Numeric Variables", "without Numeric Variables")),
       x = "Method",
       y = "Execution Time (Seconds)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") + 
  coord_flip()
  

print(p_time_comparison)

# Save time comparison plot
save_plot(p_time_comparison, "execution_time_comparison", 9, 6)
```

# Summary and Insights

```{r summary-insights, results = 'asis'}
cat("Benchmark Analysis Summary\n")
cat("=========================\n\n")

cat("Dataset:", ifelse(useRealData, "Real Clinical Data", "Synthetic Data"), "\n")
cat("Total Runs Analyzed:", nrow(all_comparison_data_for_3d_plot), "\n")
cat("Methods Evaluated:", length(unique(all_comparison_data_for_3d_plot$Method)), "\n")
cat("Subgroup Size Range:", paste(range(all_comparison_data_for_3d_plot$MinSubgroupSize), collapse = " - "), "\n")
cat("Fitness Range:", paste(round(range(all_comparison_data_for_3d_plot$OptimalFitness), 4), collapse = " - "), "\n")
cat("Time Range:", paste(round(range(all_comparison_data_for_3d_plot$Time_Seconds), 2), collapse = " - "), "seconds\n\n")

cat("Key Findings:\n")
cat("• Best performing method:", best_method, "\n")
cat("• Most efficient method:", fastest_method, "\n")
cat("• Most consistent method:", most_consistent, "\n\n")

cat("Recommendations:\n")
cat("• For maximum performance: Use", best_method, "\n")
cat("• For speed-critical applications: Use", fastest_method, "\n")
cat("• For consistent results: Use", most_consistent, "\n")
```

# Data Export

```{r data-export}
# Export summary data for further use
summary_report <- list(
  data_type = paste0(ifelse(useRealData, "real_data", "dummy_data"), "_", numeric_flag),
  timestamp = Sys.time(),
  methods_summary = methods_summary,
  total_runs = nrow(all_comparison_data_for_3d_plot),
  unique_methods = length(unique(all_comparison_data_for_3d_plot$Method)),
  subgroup_size_range = range(all_comparison_data_for_3d_plot$MinSubgroupSize),
  fitness_range = range(all_comparison_data_for_3d_plot$OptimalFitness),
  time_range = range(all_comparison_data_for_3d_plot$Time_Seconds)
)

# Save summary report
summary_file <- here::here(paste0('output/', output_subdir, '/benchmark_summary.rds'))
saveRDS(summary_report, summary_file)
```





# Stability Analysis {.tabset .tabset-pills}

This section analyzes the reproducibility and consistency of the optimization methods across multiple runs.

```{r load-stability-data}
# Check if stability raw results exist (only file we expect from run_methods.R)
stability_data_file <- here::here(paste0('output/', output_subdir, '/stability_raw_results.rds'))

if (!file.exists(stability_data_file)) {
  cat("Missing stability data file:", stability_data_file)
  cat("\nStability analysis will be skipped. Please run run_methods.R with runSim = TRUE to generate stability data.")
  stability_data_available <- FALSE
} else {
  # Load raw stability data
  all_stability_results <- readRDS(stability_data_file)
  stability_data_available <- TRUE
  
  # Transform method names to avoid confusion
  if ("Method" %in% colnames(all_stability_results)) {
    all_stability_results$Method <- gsub("Genetic Algorithm", "GA (No Quotient Space)", all_stability_results$Method)
    all_stability_results$Method <- gsub("Orbit-Aware GA", "GA (With Quotient Space)", all_stability_results$Method)
    all_stability_results$Method <- gsub("Bayesian Optimization \\(No Orbits\\)", "BO (No Quotient Space)", all_stability_results$Method)
    all_stability_results$Method <- gsub("Bayesian Optimization \\(With Orbits\\)", "BO (With Quotient Space)", all_stability_results$Method)
  }
  
  cat("Successfully loaded raw stability data:",
      sprintf("  - Raw results: %d rows", nrow(all_stability_results)),
      sep = "\n")
}
```

```{r stability-helper-functions, eval = stability_data_available}
# Generate all analysis objects from raw data (if available)
if (stability_data_available && nrow(all_stability_results) > 0) {
  # Calculate stability metrics for both fitness and solutions
  # Grouping by Method, ParamSetName, and MinSubgroupSize to account for multiple parameter sets
  stability_summary <- all_stability_results %>%
    group_by(Method, ParamSetName, MinSubgroupSize) %>%
    summarise(
      n_runs = n(),
      # Fitness stability metrics
      mean_fitness = round(mean(OptimalFitness, na.rm = TRUE), 4),
      sd_fitness = round(sd(OptimalFitness, na.rm = TRUE), 4),
      cv_fitness = round(sd(OptimalFitness, na.rm = TRUE) / mean(OptimalFitness, na.rm = TRUE) * 100, 2), # Coefficient of variation
      min_fitness = round(min(OptimalFitness, na.rm = TRUE), 4),
      max_fitness = round(max(OptimalFitness, na.rm = TRUE), 4),
      range_fitness = round(max(OptimalFitness, na.rm = TRUE) - min(OptimalFitness, na.rm = TRUE), 4),
      # Solution stability metrics
      n_unique_solutions = n_distinct(OptimalRules),
      most_common_solution_freq = max(table(OptimalRules)),
      solution_consistency_pct = round(max(table(OptimalRules)) / n() * 100, 2),
      .groups = 'drop'
    ) %>%
    arrange(Method, ParamSetName, MinSubgroupSize)
  
  # Create aggregated stability summary across all parameter sets per method
  stability_summary_aggregated <- all_stability_results %>%
    group_by(Method, MinSubgroupSize) %>%
    summarise(
      n_total_runs = n(),
      n_param_sets = n_distinct(ParamSetName),
      # Fitness stability metrics (across all parameter sets)
      mean_fitness = round(mean(OptimalFitness, na.rm = TRUE), 4),
      sd_fitness = round(sd(OptimalFitness, na.rm = TRUE), 4),
      cv_fitness = round(sd(OptimalFitness, na.rm = TRUE) / mean(OptimalFitness, na.rm = TRUE) * 100, 2),
      min_fitness = round(min(OptimalFitness, na.rm = TRUE), 4),
      max_fitness = round(max(OptimalFitness, na.rm = TRUE), 4),
      range_fitness = round(max(OptimalFitness, na.rm = TRUE) - min(OptimalFitness, na.rm = TRUE), 4),
      # Solution stability metrics (across all parameter sets)
      n_unique_solutions = n_distinct(OptimalRules),
      most_common_solution_freq = max(table(OptimalRules)),
      solution_consistency_pct = round(max(table(OptimalRules)) / n() * 100, 2),
      .groups = 'drop'
    ) %>%
    arrange(Method, MinSubgroupSize)
  
  # Create detailed solution frequency analysis
  solution_frequency_analysis <- all_stability_results %>%
    group_by(Method, ParamSetName, MinSubgroupSize, OptimalRules) %>%
    summarise(
      frequency = n(),
      mean_fitness_for_solution = round(mean(OptimalFitness), 4),
      .groups = 'drop'
    ) %>%
    group_by(Method, ParamSetName, MinSubgroupSize) %>%
    mutate(
      frequency_pct = round(frequency / sum(frequency) * 100, 2),
      rank = rank(-frequency, ties.method = "first")
    ) %>%
    arrange(Method, ParamSetName, MinSubgroupSize, rank) %>%
    ungroup()
  
  # Create a summary of unique solutions per method-paramset-size combination
  unique_solutions_summary <- solution_frequency_analysis %>%
    group_by(Method, ParamSetName, MinSubgroupSize) %>%
    summarise(
      total_unique_solutions = n(),
      most_frequent_solution = OptimalRules[1],
      most_frequent_solution_pct = frequency_pct[1],
      second_most_frequent_pct = ifelse(n() > 1, frequency_pct[2], 0),
      .groups = 'drop'
    )
  
  cat("Generated stability analysis objects from raw data:\n")
  cat(sprintf("  - Stability summary (by parameter set): %d rows\n", nrow(stability_summary)))
  cat(sprintf("  - Stability summary (aggregated): %d rows\n", nrow(stability_summary_aggregated)))
  cat(sprintf("  - Solution frequency analysis: %d rows\n", nrow(solution_frequency_analysis)))
  cat(sprintf("  - Unique solutions summary: %d rows\n", nrow(unique_solutions_summary)))
} else {
  cat("No stability data available for analysis.\n")
}
```

## Stability Overview {.tabset}

### Summary Statistics

```{r stability-overview, eval = stability_data_available}
if (exists("stability_summary_aggregated") && nrow(stability_summary_aggregated) > 0) {
  kable(stability_summary_aggregated, 
        caption = "Stability Summary - Aggregated Across All Parameter Sets",
        digits = 4) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    scroll_box(width = "100%", height = "400px")
} else {
  cat("No stability summary data available.")
}
```

### Raw Results Sample

```{r stability-raw-sample, eval = stability_data_available}
if (exists("all_stability_results") && nrow(all_stability_results) > 0) {
  # Show a sample of raw results
  sample_results <- all_stability_results %>%
    group_by(Method) %>%
    slice_head(n = 3) %>%
    ungroup()
  
  kable(sample_results, 
        caption = "Sample of Stability Raw Results (First 3 rows per method)",
        digits = 4) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    scroll_box(width = "100%", height = "400px")
} else {
  cat("No stability raw results data available.")
}
```

## Fitness Stability Visualizations {.tabset}

### Fitness Distribution

```{r stability-boxplot, eval = stability_data_available, fig.width=10, fig.height=6, results='asis'}
if (exists("all_stability_results") && nrow(all_stability_results) > 0) {
  # Get parameter set count for subtitle
  n_param_sets_to_test <- all_stability_results %>% 
    group_by(Method) %>% 
    summarise(n_param_sets = n_distinct(ParamSetName)) %>% 
    pull(n_param_sets) %>% 
    max()
  
  n_stability_runs <- all_stability_results %>% 
    group_by(Method, ParamSetName, MinSubgroupSize) %>% 
    summarise(n_runs = n(), .groups = 'drop') %>% 
    pull(n_runs) %>% 
    max()
  
  p_stability_boxplot <- ggplot(all_stability_results, aes(x = factor(MinSubgroupSize), y = OptimalFitness, col = Method)) +
    # geom_boxplot(alpha = 0.7, position = position_dodge(width = 0.8)) +
    geom_jitter(position = position_jitterdodge(dodge.width = 0.8), alpha = 0.3, size = 0.8) +
    labs(
      title = paste("Method Stability Analysis -", ifelse(useRealData, "Real Data", "Dummy Data")),
      subtitle = paste("Based on", n_stability_runs, "runs per parameter set,", n_param_sets_to_test, "parameter sets per method"),
      x = "Minimum Subgroup Size",
      y = "Optimal Fitness",
      caption = "Each point represents one run; boxes show distribution across all parameter sets"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom") + 
    facet_wrap(~Method, ncol = 3)
  
  print(p_stability_boxplot)
  
  # Save stability boxplot
  save_plot(p_stability_boxplot, "stability_fitness_distribution", 11, 6)
  
  # Prepare data for testing
  test_results <- data.frame()
  
  # Get unique MinSubgroupSize values
  subgroup_sizes <- sort(unique(all_stability_results$MinSubgroupSize))
  
  # Test GA: With Quotient Space vs No Quotient Space for each MinSubgroupSize
  for (size in subgroup_sizes) {
    # GA comparison
    ga_no_quotient_space <- all_stability_results %>% 
      filter(Method == "GA (No Quotient Space)", MinSubgroupSize == size) %>% 
      pull(OptimalFitness)
    ga_with_quotient_space <- all_stability_results %>% 
      filter(Method == "GA (With Quotient Space)", MinSubgroupSize == size) %>% 
      pull(OptimalFitness)
    
    if (length(ga_no_quotient_space) > 0 && length(ga_with_quotient_space) > 0) {
      ga_test <- wilcox.test(ga_with_quotient_space, ga_no_quotient_space, paired = FALSE)
      ga_effect_size <- (median(ga_with_quotient_space, na.rm = TRUE) - median(ga_no_quotient_space, na.rm = TRUE)) / 
                       mad(c(ga_with_quotient_space, ga_no_quotient_space), na.rm = TRUE)
      
      test_results <- rbind(test_results, data.frame(
        Method_Comparison = "GA: With Quotient Space vs No Quotient Space",
        MinSubgroupSize = size,
        n_with_quotient_space = length(ga_with_quotient_space),
        n_no_quotient_space = length(ga_no_quotient_space),
        p_value = ga_test$p.value,
        effect_size = ga_effect_size,
        median_with_quotient_space = median(ga_with_quotient_space, na.rm = TRUE),
        median_no_quotient_space = median(ga_no_quotient_space, na.rm = TRUE)
      ))
    }
    
    # BO comparison
    bo_no_quotient_space <- all_stability_results %>% 
      filter(Method == "BO (No Quotient Space)", MinSubgroupSize == size) %>% 
      pull(OptimalFitness)
    bo_with_quotient_space <- all_stability_results %>% 
      filter(Method == "BO (With Quotient Space)", MinSubgroupSize == size) %>% 
      pull(OptimalFitness)
    
    if (length(bo_no_quotient_space) > 0 && length(bo_with_quotient_space) > 0) {
      bo_test <- wilcox.test(bo_with_quotient_space, bo_no_quotient_space, paired = FALSE)
      bo_effect_size <- (median(bo_with_quotient_space, na.rm = TRUE) - median(bo_no_quotient_space, na.rm = TRUE)) / 
                       mad(c(bo_with_quotient_space, bo_no_quotient_space), na.rm = TRUE)
      
      test_results <- rbind(test_results, data.frame(
        Method_Comparison = "BO: With Quotient Space vs No Quotient Space",
        MinSubgroupSize = size,
        n_with_quotient_space = length(bo_with_quotient_space),
        n_no_quotient_space = length(bo_no_quotient_space),
        p_value = bo_test$p.value,
        effect_size = bo_effect_size,
        median_with_quotient_space = median(bo_with_quotient_space, na.rm = TRUE),
        median_no_quotient_space = median(bo_no_quotient_space, na.rm = TRUE)
      ))
    }
  }
  
  # Apply multiple testing correction (Holm's)
  if (nrow(test_results) > 0) {
    test_results$p_value_adjusted <- p.adjust(test_results$p_value, method = "holm")
    
    test_results_display = test_results %>% 
      mutate(
        p_value_formatted = format.pval(p_value, digits = 3),
        p_value_adj_formatted = format.pval(p_value_adjusted, digits = 3),
        median_difference = round(median_with_quotient_space - median_no_quotient_space, 4),
        median_difference_pct = paste0(round(median_difference/median_no_quotient_space, 4)*100, '%'),
        significance = ifelse(p_value_adjusted < 0.05, "***", 
                             ifelse(p_value_adjusted < 0.1, "*", "ns"))) %>%
      select(Method_Comparison, MinSubgroupSize, n_with_quotient_space, n_no_quotient_space, 
             median_difference, median_difference_pct,
             p_value_formatted, p_value_adj_formatted, significance)
    
    # Display results table
    print(kable(test_results_display, 
          caption = "Statistical Comparison of Quotient Space vs No-Quotient Space Methods by MinSubgroupSize",
          col.names = c("Comparison", "Min Subgroup Size", "n (With Quotient Space)", "n (No Quotient Space)", 
                       "Median Difference", "Median Difference Percentage", 
                       "p-value", "p.adj (Holm)", "Sig.")) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = TRUE) %>%
      row_spec(which(test_results_display$significance == "***"), bold = TRUE, background = "#fff2cc") %>%
      row_spec(which(test_results_display$significance == "*"), background = "#f0f0f0"))

    # Save table data for LaTeX import
    table_dir <- here::here("tables")
    if (!dir.exists(table_dir)) {
      dir.create(table_dir, recursive = TRUE)
    }
    
    # Save as CSV and TSV using the organized table directory structure
    save_table(test_results_display, "statistical_comparison_quotient_space_methods", "csv")
    
    # Save as tab-separated values for LaTeX \pgfplotstableread
    tsv_filename <- "statistical_comparison_quotient_space_methods.tsv"
    write.table(test_results_display, file.path(tables_dir, tsv_filename), 
                sep = "\t", row.names = FALSE, quote = FALSE)
    cat("Saved table:", file.path(tables_dir, tsv_filename), "\n")
  } else {
    cat("No valid comparisons could be performed (insufficient data).\n")
  }
} else {
  cat("No stability data available for boxplot visualization.")
}
```



### Coefficient of Variation

```{r stability-cv, eval = stability_data_available, fig.width=10, fig.height=6}
if (exists("stability_summary_aggregated") && nrow(stability_summary_aggregated) > 0) {
  n_param_sets_to_test <- max(stability_summary_aggregated$n_param_sets, na.rm = TRUE)
  
  p_stability_cv <- ggplot(stability_summary_aggregated, aes(x = factor(MinSubgroupSize), y = cv_fitness, fill = Method)) +
    geom_col(position = "dodge", alpha = 0.7) +
    geom_text(aes(label = paste0(cv_fitness, "%")), 
              position = position_dodge(width = 0.9), 
              vjust = -0.3, size = 3) +
    labs(
      title = "Method Stability: Fitness Coefficient of Variation",
      subtitle = paste("Aggregated across", n_param_sets_to_test, "parameter sets (lower = more stable)"),
      x = "Minimum Subgroup Size",
      y = "Coefficient of Variation (%)",
      fill = "Method"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  print(p_stability_cv)
  
  # Save stability CV plot
  save_plot(p_stability_cv, "stability_coefficient_variation", 11, 6)
} else {
  cat("No stability CV data available for visualization.")
}
```

## Solution Consistency Visualizations {.tabset}


### Unique Solutions Count

```{r stability-unique, eval = stability_data_available, fig.width=10, fig.height=6}
if (exists("stability_summary_aggregated") && nrow(stability_summary_aggregated) > 0) {
  n_param_sets_to_test <- max(stability_summary_aggregated$n_param_sets, na.rm = TRUE)
  n_stability_runs <- max(stability_summary_aggregated$n_total_runs / stability_summary_aggregated$n_param_sets, na.rm = TRUE)
  
  p_unique_solutions <- ggplot(stability_summary_aggregated, aes(x = factor(MinSubgroupSize), y = n_unique_solutions, fill = Method)) +
    geom_col(position = "dodge", alpha = 0.7) +
    geom_text(aes(label = n_unique_solutions), 
              position = position_dodge(width = 0.9), 
              vjust = -0.3, size = 3) +
    labs(
      title = "Method Stability: Number of Unique Solutions",
      subtitle = paste("Across", n_param_sets_to_test, "parameter sets ×", n_stability_runs, "runs (lower = more consistent)"),
      x = "Minimum Subgroup Size",
      y = "Number of Unique Solutions",
      fill = "Method"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  print(p_unique_solutions)
  
  # Save unique solutions plot
  save_plot(p_unique_solutions, "stability_unique_solutions", 11, 6)
} else {
  cat("No unique solutions data available for visualization.")
}
```




# Export methods summary as CSV

```{r}
# Save to output directory (for compatibility with run_methods.R)
csv_file <- here::here(paste0('output/', output_subdir, '/benchmark_results.csv'))
write.csv(methods_summary, csv_file, row.names = FALSE)

# Also save to tables subdirectory for organized storage
table_csv_file <- save_table(methods_summary, "methods_summary", "csv")
table_rds_file <- save_table(methods_summary, "methods_summary", "rds")

cat("Summary data exported to:\n")
cat("•", summary_file, "\n")
cat("•", csv_file, "\n")
cat("•", table_csv_file, "\n")
cat("•", table_rds_file, "\n")

# Summary of saved plots
cat("\nPlots saved to:", plots_dir, "\n")
plot_files <- list.files(plots_dir, full.names = FALSE)
if (length(plot_files) > 0) {
  cat("Generated plot files:\n")
  for (file in plot_files) {
    cat("•", file, "\n")
  }
} else {
  cat("No plot files found for current data type.\n")
}

# Summary of tables
cat("\nTables saved to:", tables_dir, "\n")
table_files <- list.files(tables_dir, full.names = FALSE)
if (length(table_files) > 0) {
  cat("Generated table files:\n")
  for (file in table_files) {
    cat("•", file, "\n")
  }
} else {
  cat("No table files found.\n")
}

# Overall summary
cat("\n" , rep('=', 60), "\n")
cat("ORGANIZED OUTPUT SUMMARY FOR:", toupper(output_subdir), "\n")
cat(rep('=', 60), "\n")
cat("📊 Data files:", paste0("output/", output_subdir, "/"), "\n")
cat("📈 Plot files:", plots_dir, "\n") 
cat("📋 Table files:", tables_dir, "\n")
cat("📄 Report file:", reports_dir, "\n")
cat(rep('=', 60), "\n")
```

---

*Report generated on `r Sys.time()` using R version `r R.version.string`*
